---
title: "Analyses"
author: "Yrian Derreumaux"
date: "5/19/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#knitr::opts_knit$set(root.dir = '/tmp')
```

```{r}
library(ordinal)
library(ggeffects)
library(dplyr)
library(broom)
library(sjPlot)
```


# Check Packages 

```{r}
#snapshot shows all libraries #https://rstudio.github.io/packrat/walkthrough.html
#packrat::snapshot()
```

# get data
```{r}
#accessing data from google drive
#authenticate 
# drive_auth()
#check account accessed
# drive_user()

#uncomment below if we want to download to local repository
#locate folder with data
#file_url <- "https://drive.google.com/drive/u/1/folders/1lKMwv_Xf7AGQO5fuSwTlPbzV9Vr6lqLt/SharedDFfullDF.csv"
#save id
#to save files to local repository
# folder <- drive_get(as_id(file_url))
# csv_files <- drive_ls(folder, type = "csv")
# walk(csv_files$id, ~ drive_download(as_id(.x)))

#below to read in from google drive but not download
df <- read.csv("../input/PFfullDF.csv")
df <- subset(df, Info == "Info")
```

# demographics
```{r}
#number of participants
length(unique(df$subID))
#affiliation
prop.table(table(as.factor(df$Polit)))
```


```{r}
df$Polit <- ordered(df$Polit)
df$WSCz <- scale(df$WSC)
df$SES <- ordered(df$SES)
df$MLAMz <- scale(df$MLAM)
df$eval <- as.factor(df$eval)
df$affPolZ <- scale(df$affPol)
df$inMinOutZ <- scale(df$inMinOut)
```


```{r}
varReduced <- function(reference, compare){
  output <- (reference - compare)/reference
  return(output)
}
```


# Information and Polling Approval

## Null Model: One-Way ANOVA

```{r}
null <-  clmm(as.factor(eval) ~ 1 + (1|subID) + (1|issues), data = df, threshold = "flexible")
tidy(null,conf.int=TRUE,exponentiate=TRUE,effects="fixed")
summary(null)

performance::icc(null)

Null.COV <- VarCorr(null)
Null.InterceptVar.SubID <- Null.COV$subID[1]
Null.InterceptVar.Issues <- Null.COV$issues[1]
```

## Means-As-Outcomes: i.e., L1-Only with Fixed Slopes

```{r}
ANCOVA <-  clmm(as.factor(eval) ~ scale(inMinOut) + (1|subID) + (1|issues), data = df, threshold = "flexible")
tidy(ANCOVA,conf.int=TRUE,exponentiate=TRUE,effects="fixed")

performance::icc(ANCOVA)

ANCOVA.VCOV <- VarCorr(ANCOVA)
ANCOVA.InterceptVar.SubID <- ANCOVA.VCOV$subID[1]
ANCOVA.InterceptVar.Issues <- ANCOVA.VCOV$issues[1]
```

### # Intercept Variance Reduced for People

```{r}
varReduced(Null.InterceptVar.SubID, ANCOVA.InterceptVar.SubID)
```

### # Intercept Variance Reduced for Issues

```{r}
varReduced(Null.InterceptVar.Issues, ANCOVA.InterceptVar.Issues)
```

## Random Coefficient: i.e., L1-Only with Random Slopes

```{r}
Ran <-  clmm(as.factor(eval) ~ scale(inMinOut) + (scale(inMinOut)|subID) + (1|issues), data = df, threshold = "flexible")
tidy(Ran,conf.int=TRUE,exponentiate=TRUE,effects="fixed")

performance::icc(Ran)

Ran.VCOV <- VarCorr(Ran)
Ran.InterceptVar.SubID <- Ran.VCOV$subID[1]
Ran.InterceptVar.Issues <- Ran.VCOV$issues[1]


Ran.SlopeVar.SubID <- Ran.VCOV$subID[4]
Ran.SlopeVar.Issues <- Ran.VCOV$issues[4]
```

### # Intercept Variance Reduced for People

```{r}
varReduced(ANCOVA.InterceptVar.SubID, Ran.InterceptVar.SubID)
```

### # Intercept Variance Reduced for Issues

```{r}
varReduced(ANCOVA.InterceptVar.Issues, Ran.InterceptVar.Issues)
```

## Means-and-slopes-as-outcomes: i.e., L1 with Random Slopes and L2 cross-level

```{r}
MASAO <-  clmm(eval ~ affPolZ * inMinOutZ + ( inMinOutZ |subID) + (1|issues), data = df, threshold = "flexible")
tidy(MASAO,conf.int=TRUE,exponentiate=TRUE,effects="fixed")

performance::icc(MASAO)

MASAO.VCOV <- VarCorr(MASAO)
MASAO.InterceptVar.SubID <- MASAO.VCOV$subID[1]
MASAO.InterceptVar.Issues <- MASAO.VCOV$issues[1]

MASAO.SlopeVar.SubID <- MASAO.VCOV$subID[4]
MASAO.SlopeVar.Issues <- MASAO.VCOV$issues[4]
```

### # Intercept Variance Reduced for People

```{r}
varReduced(Ran.InterceptVar.SubID, MASAO.InterceptVar.SubID)
```

### # Intercept Variance Reduced for Issues

```{r}
varReduced(Ran.InterceptVar.Issues, MASAO.InterceptVar.Issues)
```

### # Slope Variance Reduced for People

```{r}
varReduced(Ran.SlopeVar.SubID, MASAO.SlopeVar.SubID)
```

```{r}
tab_model(null, ANCOVA, Ran, MASAO, show.stat=T, show.r2 = T, show.se = T, show.ci = F, show.p = F, pred.labels = c("1|2","2|3","3|4","4|5","5|6","6|7","Approval","Polarized", "Polarized*Approval"), string.pred = c("Fixed Effects"), string.est = "OR", string.se = "SE", string.stat = "z", digits = 2, emph.p = F, dv.labels = c("Null","MAO","ANCOVA","MASAO"), file="./EDUC215Dtable.doc")
```

```{r}
tab_model(null, MAO, ANCOVA, MASAO, show.stat=T, show.r2 = T, show.se = T, show.ci = F, show.p = T, pred.labels = c("1|2","2|3","3|4","4|5","5|6","6|7","Approval","Polarized", "Polarized*Approval"), string.pred = c("Fixed Effects"), string.est = "OR", string.se = "SE", string.stat = "z", digits = 2, emph.p = F, dv.labels = c("Null","MAO","ANCOVA","MASAO") )
```

```{r}
anova(null, MAO, ANCOVA, MASAO)
```
# Plot

```{r}
plot <- ggpredict(MASAO, c("inMinOutZ", "affPolZ")) %>% plot(show.title=F) + jtools::theme_apa() 
plot$labels$x <- "Ingroup - Outgroup Approval"
plot$labels$y <- "Support"
plot
```


## Means-and-slopes-as-outcomes: i.e., L1 with Random Slopes and L2 cross-level

With more predictors

```{r}
MASAO2 <-  clmm(eval ~ affPolZ * inMinOutZ + WSCz * inMinOutZ + MLAMz * inMinOutZ + Polit * inMinOutZ +  ( inMinOutZ |subID) + (1|issues), data = df, threshold = "flexible")
tidy(MASAO2,conf.int=TRUE,exponentiate=TRUE,effects="fixed")

performance::icc(MASAO2)

MASAO2.VCOV <- VarCorr(MASAO2)
MASAO2.InterceptVar.SubID <- MASAO2.VCOV$subID[1]
MASAO2.InterceptVar.Issues <- MASAO2.VCOV$issues[1]

MASAO2.SlopeVar.SubID <- MASAO2.VCOV$subID[4]
MASAO2.SlopeVar.Issues <- MASAO2.VCOV$issues[4]
```

### # Intercept Variance Reduced for People

```{r}
varReduced(MASAO.InterceptVar.SubID, MASAO2.InterceptVar.SubID)
```

### # Intercept Variance Reduced for Issues

```{r}
varReduced(MASAO2.InterceptVar.SubID, MASAO2.InterceptVar.SubID)
```

### # Slope Variance Reduced for People

```{r}
varReduced(MASAO.SlopeVar.SubID, MASAO2.SlopeVar.SubID)
```

```{r}
df2<-df[complete.cases(df$Polit),]
df2<-df2[complete.cases(df2$WSC),]
df2<-df2[complete.cases(df2$MLAM),]

null2 <-  clmm(as.factor(eval) ~ 1 + (1|subID) + (1|issues), data = df2, threshold = "flexible")

anova(null, MASAO2)
```

```{r}
tab_model(MASAO2, show.stat=T, show.r2 = T, show.se = T, show.ci = F, show.p = F, string.pred = c("Fixed Effects"), string.est = "OR", string.se = "SE", string.stat = "z", digits = 2, emph.p = F, dv.labels = c("MASAO"), file="./EDUC215DtableEXPANDED.doc")

#pred.labels = c("1|2","2|3","3|4","4|5","5|6","6|7","Approval","Polarized", "Polarized*Approval"),
```



